% star needed to make sure that the 'acknowledgments' are not included in chapter numbering
\chapter{Acknowledgments}


shatennu

vivek

request quick- summit

It has been a long way since I joined Rice as a grad student back in 2013. Over the past
(many) years I have been through a lot and, most importantly, I have met wonderful people
who, together with the unconditional support of my family, have helped me grow professionally
and personally: it just so happens that a lot of them are fellow Italians, and those
I prefer to acknowledge later in our native language.
First thing first, I would like to show my gratitude to Cecilia. She oered me the opportunity
to start such a long journey in a top-tier grad school like Rice University, which
turned out to be crucial for my professional growth. Under her advice, I got to doing high
quality research, traveling and presenting my work; also, she relentlessly encouraged me to
raise the bar by setting the example and (not to be underestimated) took me to task during
my occasional goof times. She has really been an incredible mentor.
I would also like to thank Matteo and Tolya for agreeing to sitting on my PhD defense
committee and for the insightful feedback they provided at the time of my Qualifying Exam.
Many thanks to Frank for being a great collaborator and for being always willing to help.
I would like to acknowledge all the previous and current lab mates for sharing the ride
down this very bumpy road. Mary and Wenwei were my first official lab mates, and they
helped me a lot get started with coding and other technicalities to which I had never been
really exposed before. Justin and Feliks have recently shared joys and frustration over the
last few years, especially during those less happy moments when I had no idea if I would
ever graduate.
Thanks to Dr. Gianpaolo Gobbo, Dr. Ralf Banisch and Dr. Feliks Nuske for collaboviii
rating with me on the dierent research projects.
Last but not least, I really have to thank Tim, Wei, John, Behnaam and Jesse, my
volleyball buddies. We have played so many games over the weeks, we have put in so many
hours of fun, and I have loved every minute of that. They truly are great friends to share a
volleyball court and to win Intramural Championships (twice!) with. I will miss them all.
